
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}
  {\vspace{-4pt}\scshape\raggedright\large}
  {}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1\vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Igor Janotti} \\ \vspace{1pt}
  \small (425)~638--3519 $|$
    \href{mailto:IgorJ1@live.com}{IgorJ1@live.com} $|$
  \href{https://github.com/IgorJanGit}{github.com/IgorJanGit}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
Computer Science student graduated in June 2026 with a focus on backend development and data management. I thrive in collaborative environments where I can apply my problem-solving skills to real-world challenges. I’m passionate about building efficient, scalable systems and contributing to impactful software, and I have multiple project experiences that relates on energy and waste system.
%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
  \item{
    \textbf{Languages}: Java, Python, C/C++, C\#, JavaScript/TypeScript \\
    \textbf{Cloud \& Systems}: AWS, Docker, Event-Driven Architecture \\
    \textbf{Tooling}: Git, GitHub Actions, Node.js, PydanticAI \\
    \textbf{Databases}: MySQL, MongoDB \\
    \textbf{Core Concepts}: OOP, Data Structures, Algorithms, Full-Stack Development
  }
}
\end{itemize}



%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Pacific Northwest National Laboratory (Department of Energy)}{Jun 2025 -- May 2026}
    {Software Engineer Intern}{}
    \resumeItemListStart
      \resumeItem{Contributed to VOLTTRON Eclipse, an open-source, agent-based platform for distributed energy and building systems.}
      \resumeItem{Worked with modular, event-driven architectures to improve scalability and system reliability.}
      \resumeItem{Collaborated with researchers and engineers in an Agile environment.}
    \resumeItemListEnd

  \resumeSubheading
    {Bellevue College}{Feb -- Mar 2024}
    {Teaching Assistant -- Programming Languages (C++)}{}
    \resumeItemListStart
      \resumeItem{Supported students with C++, CMake, Google Test, Ninja, and GitHub Actions.}
      \resumeItem{Reviewed code, assisted with debugging, and reinforced core programming concepts.}
      \resumeItem{Helped students understand testing, compilation pipelines, and version control.}
    \resumeItemListEnd

  \resumeSubheading
    {CodeDay}{Nov -- Dec 2024}
    {Micro Intern -- Appwrite}{Remote}
    \resumeItemListStart
      \resumeItem{Translated Node.js templates to Python for Appwrite, an open-source backend platform with 75K+ monthly users.}
      \resumeItem{Converted GitHub Issue Bot template to Python, expanding platform support.}
      \resumeItem{Led peer code reviews and contributed to documentation standardization.}
      \resumeItem{Acted as Scrum Master, facilitating sprint planning and retrospectives.}
    \resumeItemListEnd

  \resumeSubheading
    {CodeDay -- Open Energy Dashboard}{Jan -- Feb 2024}
    {Micro Intern}{Remote}
    \resumeItemListStart
      \resumeItem{Developed automated function tests using Mocha and Chai for an existing production codebase.}
      \resumeItem{Used Docker for containerization and GitHub for collaboration and CI workflows.}
      \resumeItem{Gained experience working with unfamiliar technologies and large-scale repositories.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Eclipse VOLTTRON} $|$ \emph{Python, BACnet, PydanticAI, CLI Tools}}{}
      \resumeItemListStart
        \resumeItem{Contributed to Eclipse VOLTTRON, an open-source, agent-based platform for distributed energy and building systems at PNNL.}
        \resumeItem{Developed a BACnet scanner to improve device discovery and system observability.}
        \resumeItem{Built an AI-driven CLI interpreter to simplify command-line interaction and improve developer usability.}
        \resumeItem{Worked in a research-driven, modular architecture on a large-scale open-source codebase.}
    \resumeItemListEnd


  \resumeProjectHeading
    {\textbf{FollowBot Companion Robot} $|$ \emph{C++, Python, JavaScript}}{}
    \resumeItemListStart
      \resumeItem{Developed a companion robot featuring mapping, pathfinding, and obstacle avoidance.}
      \resumeItem{Worked across frontend, backend, and database components.}
      \resumeItem{Planned migration to ROS2 for improved robotics integration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{AWS License Plate Recognition System} $|$ \emph{C\#, AWS}}{}
    \resumeItemListStart
      \resumeItem{Built an automated fine-processing system using AWS Rekognition, Lambda, DynamoDB, and SNS.}
      \resumeItem{Enabled real-time email notifications for detected license plates.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Food Item Expiration Tracker} $|$ \emph{Python}}{}
    \resumeItemListStart
      \resumeItem{Designed a database-driven system to track food expiration dates.}
      \resumeItem{Implemented email alerts with plans for background service deployment.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Bellevue College}{Bellevue, WA}
    {Bachelor of Science in Computer Science}{2023 -- Spring 2025}
    \resumeItemListStart
      \resumeItem{GPA: 3.54}
      \resumeItem{Relevant Coursework: Software Engineering, Cloud Computing, Data Structures, Algorithms, Database Systems}
    \resumeItemListEnd

  \resumeSubheading
    {Bellevue College}{Bellevue, WA}
    {Associate of Arts \& Science}{2019 -- 2023}
    \resumeItemListStart
      \resumeItem{GPA: 3.69}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
  \item{
    \textbf{Awards}: NEXTGEN Startup Challenge (2nd Place), Ready Tensor Computer Vision Expo 2024 (Most Promising Innovation), GameJam Bellevue College (Best Mechanics) \\
    \textbf{Certification}: Git
  }
}
\end{itemize}

\end{document}
